---
title: "Virtual East Coast Trail Run/Walk"
html_document:
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(gsheet)
library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
```

```{r data}
# grabing data from google documents

data<-gsheet2tbl('docs.google.com/spreadsheets/d/1Ji5gLBc8HbbEogKwV3yFj9MWn80Kw9jpFnMKsGzc-Jo')
total<-read.csv("totalDIS.csv")

data<-data %>% 
  mutate(Date = mdy(Date))

total_km<-sum(total$Length.KM)
total_m<-sum(total$Gain, na.rm = T)

r_date<-min(data$Date)
```

This is an update of our progress as we try and run and walk the equivelent distance of the East Coast Trail which runs from Topsail to Cappahadyen in Newfoundland. The total distance is `r total_km`km and the total elevation is `r total_m`m.

Enter your runs and walks at [here](https://forms.gle/tNduBU5ztHg4K8uG7).

The most recent activity included in this update is `r r_date`.

## Are we there yet?

Percentage of our total goal completed to date:

```{r pressure, echo=FALSE}
p1<-data %>% 
  summarise(km_completed = sum(Distance_km),
            m_completed = sum(Elevation.gain_m),
            p_distance = km_completed/total_km*100,
            p_elevation = m_completed/total_m*100) %>% 
  pivot_longer(names_to = "metric", values_to = 'N',cols = starts_with("p_")) %>% 
  ggplot(aes(x=metric, y=N)) +
  geom_segment( aes(x=metric, xend=metric, y=0, yend=N), color="skyblue") +
  geom_point( color="blue", size=4, alpha=0.6) +
  theme_light() +
  scale_y_continuous(limits = c(0,100))+
  scale_x_discrete(labels = c("Elevation (m)","Distance (km)"))+
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )+
  ylab("Percent Completed")+xlab("")

ggplotly(p1)
```

## Where are we going?

There is a break down of all the segements of the ECT. There are many sections of road between the trail. We are going the entire distance, just like a through hike! There is missing elevation measurements but those are mostly the new sections.

```{r}
total %>%
  select(Path.Name...Type,Length.KM,Gain) %>% 
  rename('Path Name' = Path.Name...Type,
         'Length (km)' = Length.KM,
         'Elevation gain (m)' = Gain) %>% 
  DT::datatable( editable = 'cell')
```

